\documentclass[a4paper,12pt]{article}
\usepackage{fontspec} % Required for specifying the font
%\setmainfont{EB Garamond} % Specifies EB Garamond as the main font
\usepackage{hyperref} % For hyperlinks
\hypersetup{
    colorlinks=true,
    linkcolor=black,
    urlcolor=black,
    citecolor=black,
    filecolor=black
}
\usepackage{geometry} % For setting page dimensions
\usepackage{enumitem} % For customizing lists
\usepackage{graphicx} % For including images
\geometry{margin=1in} % Set margins
\usepackage{titlesec} % For title formatting
\usepackage{array} % For table customization
\usepackage{fontawesome} % For icons
\usepackage{xcolor} % For icon colors
\usepackage{ragged2e}
\usepackage[bb=boondox,bbscaled=.95,cal=boondoxo]{mathalfa} 
\usepackage{fancyhdr}
\usepackage[yyyymmdd,hhmmss]{datetime}
\usepackage{helvet}
\definecolor{themecolor}{RGB}{225,50,10}

% Set up page header/footer for "Last Updated" information
\fancypagestyle{lastupdate}{
    \fancyhf{}
    \fancyfoot[R]{Last Updated: \today}
    \renewcommand{\headrulewidth}{0pt}
    \renewcommand{\footrulewidth}{0.4pt}
}

% Define section formatting
\titleformat{\section}{
      \color{themecolor}\vspace{-2pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{themecolor}\titlerule \vspace{-5pt}]
\titleformat{\subsection}{\normalsize\bfseries}{}{0em}{}

% Reduce space between items in lists
\setlist{nosep}

% Adjust space between sections and paragraphs
\titlespacing*{\section}{0pt}{*2}{*2}
\setlength{\parskip}{6pt}

\newcommand{\sectionspace}{0pt} % additional space between each section
\newcommand{\itemspace}{7pt} % space between each item

\begin{document}
\sloppy % Allow for more flexible line breaks

\begin{center}
    \vspace*{-50pt} % Force reduce top margin even more
    \textbf{{\fontsize{25}{48}\selectfont F}{\fontsize{18}{48}\selectfont ENG-}{\fontsize{25}{48}\selectfont C}{\fontsize{18}{48}\selectfont HUN }{\fontsize{25}{48}\selectfont B}{\fontsize{18}{48}\selectfont EN} {\fontsize{25}{48}\selectfont C}{\fontsize{18}{48}\selectfont HOU}} \\
    \vspace{10pt} % Reduce spacing after name
    \href{https://github.com/Ben-FCC}{\color{black}\faGithub \ Ben-FCC} \\
    \href{https://scholar.google.com/citations?user=oZ5rsb0AAAAJ&hl=en}{\color{black}\faGoogle \ Google Scholar}\\
    \href{mailto:f11227106@ntu.edu.tw}{\color{black}\faEnvelope \ f11227106@ntu.edu.tw} \\
    \href{https://x.com/FengChunChou}{$\mathbb{X}$ \@FengChunChou}\\
    \href{https://www.researchgate.net/profile/Feng-Chun-Chou-2?ev=hdr_xprf}{$\mathbb{R}^{\mathbb{G}}$ ResearchGate}\\
\end{center}

\vspace{5pt}

\section*{ABOUT ME}
I am currently a PhD student under supervision by \href{https://scholar.google.com/citations?hl=en&user=wXNCX4EAAAAJ&view_op=list_works&sortby=pubdate}{Andy Chen} at \href{https://www.chenlaboratory.com/}{CHENLab}. My research interests focus on using various multimodal methods (e.g., fMRI, Social Network, Nonverbal behavior, etc.) combined with \href{https://naturalistic-data.org/content/intro.html}{Naturalistic Paradigms} to deconstruct the complex mechanisms behind \href{https://cosanlab.com/static/papers/Wheatley_2023_PISP.pdf}{Interacting Minds} and understand the emergent properties generated by human interactions.
\vspace{\sectionspace}

\section*{EDUCATION}

\begin{flushright}
\begin{tabular}{@{}p{0.65\textwidth}@{}p{0.35\textwidth}@{}}
    \textbf{National Taiwan University, Taipei, Taiwan} & \hfill 2023 - present \\
    Ph.D. in Psychology & \\[6pt]
    \textbf{National Taiwan University, Taipei, Taiwan} & \hfill 2017 - 2022 \\
    B.Sc. in Physics & \\
\end{tabular}
\end{flushright}

\section*{AWARDS AND HONORS}
\begin{flushright}
\begin{tabular}{@{}p{0.65\textwidth}@{}p{0.35\textwidth}@{}}
\href{https://www.sinica.edu.tw/en/News_Content/56/2728}{Academia Sinica Fellowship for Elite Ph.D. in HSS} & \hfill 2024 - 2028 \\[2pt]
\href{https://www.tpa-tw.org/post/2024travel-grant}{TPA Annual Conference Yang Kuo-Shu Travel Grants} & \hfill 2024\\[2pt]
\href{https://socialaffectiveneuro.org/wp-content/uploads/2024/05/SANS-Conference-2024_Program_Final.pdf}{SANS Annual Conference Datablitz Talk} & \hfill 2024\\[2pt]
\href{https://www.nstc.gov.tw/sci/ch/detail/259f99f5-51ce-4582-8546-9d7caee96871}{NSTC Student Travel Award}  & \hfill 2024\\[2pt]
\href{https://www.science.ntu.edu.tw/file/rule50.pdf}{NTU College of Science Doctoral Scholarship}  & \hfill 2024 - 2025\\[2pt]
\href{https://ord.ntu.edu.tw/w/ordntu/GW_20072012180521920/}{NTU Doctoral Scholarship}  & \hfill 2023 - 2025\\[2pt]
\end{tabular}
\end{flushright}

\vspace{\sectionspace}

\section*{PUBLICATIONS}
\textit{* indicates co-first authorship.} \\[10pt]
\noindent \textbf{Chou, F.-C. B.,*} \& Chen, P.-H. A.* (2025). Beyond dyadic interaction and shared experience: rethinking social connections. \textit{Psychology of Learning and Motivation}. \href{https://10.1016/bs.plm.2025.03.002}{https://doi.org/10.1016/bs.plm.2025.03.002} \\[\itemspace]
\noindent\textbf{Chou, F.-C. B.,*} Chen, Y.-C. C.,* Kuo, Y.-S. A., Hsiao, P.-Y. A., Lin, C. R., Huang, Y.-W. Y., Peng, W.-L., Pan, H.-J. S., \& Chen, P.-H. A. (2025). Facial insights: An exploration of similarity in spontaneous facial behaviors during pandemic lockdown. \textit{Technology, Mind, and Behavior}, 6(2). \href{https://doi.org/10.1037/tmb0000166}{https://doi.org/10.1037/tmb0000166} \\[\itemspace]
\noindent Chen, P.-H. A., Chiu, T.-A. P., Hsiao, P.-Y. A., \& \textbf{Chou, F.-C. B.} (2025). From experiences to preferences: neural insights through a naturalistic neuroimaging paradigm. In Fareri, D., Smith, D. \& Lockwood, P. (Eds.), \textit{Neuroeconomics: Core Topics and Current Directions.} Springer Nature.\\[\itemspace]
\noindent Hsiao, P.-Y. A., Kim, M. J., \textbf{Chou, F.-C. B.}, \& Chen, P.-H. A. (2024). Intersubject representational similarity analysis uncovers the impact of state anxiety on brain activation patterns in the human extrastriate cortex. \textit{Brain Imaging and Behavior}, 18(2), 1-9. \href{https://doi.org/10.1007/s11682-024-00854-1}{https://doi.org/10.1007/s11682-024-00854-1}
\\[\itemspace]

\section*{MANUSCRIPTS UNDER REVIEW}
\noindent Chen, P.-H. A.,* \textbf{Chou, F.-C. B.,*} \& Wang, T.-R. H.* (Under revision). Rethinking acculturation: placing social interaction at the center of cultural adaptation.\\[\itemspace]
\noindent \textbf{Chou, F.-C. B.,*} Chang, C.-Y. E.,* Lee, W.-T. W., Chang, J.-H., \& Chen, P.-H. A. (Under review). Friendship in Mind: Linking mental representations of friendships to well-being.\\[\itemspace]

\vspace{\sectionspace}

\section*{INVITED TALKS}
\textbf{Symposium Talk}, Simultaneous Collection of Multimodal Measures Reveals Unique Facets of Affective Experience. \textit{Taiwanese Psychological Association 2025 Annual Conference}, Tainan, Taiwan \\[\itemspace]
\textbf{Seminar Talk}, \href{http://www.psy.ntu.edu.tw/index.php/homepage/speech/2903-1131127}{Decoding Preferences: Neural Mechanisms Linking Appraisal to Choice.} \textit{Department of Psychology, National Taiwan University}, Taipei, Taiwan \\[\itemspace]
\textbf{Award Talk}, \href{https://github.com/Ben-FCC/Ben-FCC_CV/blob/main/assets/2024_TPA_Oral.pdf}{From divergent opinions to aligned impressions: The power of shared experiences.}  \textit{Taiwanese Psychological Association 2024 Annual Conference}, Taipei, Taiwan \\[\itemspace]
\textbf{Symposium Talk}, From divergent opinions to aligned impressions: The power of shared experiences.  \textit{Taiwanese Psychological Association 2024 Annual Conference}, Taipei, Taiwan \\[\itemspace]
\textbf{Blitz Topic},  From Opposing Views to Aligned Impressions: Shared Experiences Matter.  \textit{Social \& Affective Neuroscience Society 2024 Annual Conference}, Toronto, Canada \\[\itemspace]
\textbf{Symposium Talk}, Intersubject representational similarity analysis uncovers individual variations in experiencing effortful self-control. \textit{Taiwanese Society of Cognitive Neuroscience 2023 Annual Conference}, Taoyuan, Taiwan \\[\itemspace]
\textbf{Symposium Talk}, Intersubject representational similarity analysis uncovers individual variations in experiencing effortful self-control.  \textit{12\textsuperscript{th} Conference for Chinese Psychologists}, Taipei, Taiwan \\[\itemspace]
\textbf{Symposium Talk}, Intersubject representational similarity analysis uncovers individual variations in experiencing effortful self-control.  \textit{Taiwanese Psychological Association 2023 Annual Conference}, Hsinchu, Taiwan \\[\itemspace]

\vspace{\sectionspace}

\section*{PUBLIC ENGAGEMENT \& MEDIA}
\noindent\textbf{Podcast Guest}, How Does Anxiety Shape Your Worldview? \textit{Reveal}, Taipei, Taiwan (2025-09-03). \href{https://podcasts.apple.com/tw/podcast/%E9%87%8D%E6%95%B4%E8%A9%95%E4%BC%B0/id1747099567?l=en-GB&i=1000724790000}{S4E4} \\[\itemspace]

\vspace{\sectionspace}

\section*{CONFERENCE PRESENTATIONS}
\noindent\textbf{Chou, F.-C. B.}, Chang, C.-Y. E., Lee, W.-T. W., Chang, J.-H., \& Chen, P.-H. A. (2025). Unpacking the association of mental representations of friendship and well-being through the Anna Karenina Principle. \textit{Social \& Affective Neuroscience Society 2025 Annual Conference}, Chicago, USA. \\[\itemspace]
\noindent\textbf{Chou, F.-C. B.}, Chiu, T.-A. P., Hsiao, P.-Y. A., Chang, C.-Y. E., \& Chen, P.-H. A. (2024). Unraveling the neural representations of preference with a naturalistic neuroimaging approach. \textit{Cognitive Neuroscience Society 2024 Annual Meeting}, Toronto, Canada.\\[\itemspace]
\noindent\textbf{Chou, F.-C. B.}, Kuo, Y.-S. A., Chen, Y.-C. C., Chang, C.-Y. E., \& Chen, P.-H. A. (2024). From Opposing Views to Aligned Impressions: Shared Experiences Matter. \textit{Social \& Affective Neuroscience Society 2024 Annual Conference}, Toronto, Canada. \\[\itemspace]
\noindent\textbf{Chou, F.-C. B.}, Hsiao, P.-Y. A., Jolly, E., Chang, L.J., \& Chen, P.-H. A. (2022). Taking a naturalistic neuroimaging approach to examine shared responses across cultures. \textit{Social \& Affective Neuroscience Society 2022 Virtual Conference}.\\[\itemspace]
\noindent\textbf{Chou, F.-C. B.}, Pan, H.-J. S., Huang, Y.-W. Y., Kuo, Y.-S. A., Chen, Y.-C. C., Hsiao, P.-Y. A., Lin, C. R., \& Chen, P.-H. A. (2022). Collective synchronization of emotional expressions under a large-scale social stressor. \textit{Society for Affective Science 2022 Virtual Conference}.\\[\itemspace]

\vspace{\sectionspace}

\section*{MENTORING EXPERIENCE}
\noindent Hsu, C.-H. H., \textbf{Chou, F.-C. B.}, Wang, T.-R. H., Wang, S.-C. T., \& Chen, P.-H. A. (2025). Using brain functional connectome to predict political attitudes. \textit{Taiwanese Psychological Association 2025 Annual Conference}, Tainan, Taiwan. \\[\itemspace]
\noindent Wang, S.-C. T., \textbf{Chou, F.-C. B.}, \& Chen, P.-H. A. (2025). Cross-modality correspondence between mental and behavioral representations of impressions in virtual reality. \textit{Taiwanese Psychological Association 2025 Annual Conference}, Tainan, Taiwan. \\[\itemspace]
\noindent Wang, T.-R. H., \textbf{Chou, F.-C. B.}, \& Chen, P.-H. A. (2025). Not all friendships look alike: Positive affect and mental representations of friendship in collectivist cultures. \textit{Taiwanese Psychological Association 2025 Annual Conference}, Tainan, Taiwan. \\[\itemspace]
\noindent Lin, C.-H. J., \textbf{Chou, F.-C. B.}, \& Chen, P.-H. A. (2025). Inhibitory training impacts the transition probability across multiple temptation-related states and actions. \textit{Taiwanese Psychological Association 2025 Annual Conference}, Tainan, Taiwan. \\[\itemspace]
\noindent Lin, C.-C. E., \textbf{Chou, F.-C. B.}, Chou, T.-C. K., Wang, T.-R. H., \& Chen, P.-H. A. (2025). Examining the test-retest reliability of MBTI: From total scores to response patterns, with comparisons to the Big Five Inventory. \textit{Taiwanese Psychological Association 2025 Annual Conference}, Tainan, Taiwan. \\[\itemspace]
\noindent Chen, J., \textbf{Chou, F.-C. B.}, Jao, C.-Y. M., Wang, T.-R. H., Wang, S.-C. T., \& Chen, P.-H. A. (2025). Using heart rate dynamics to examine emotional adaptation during prolonged naturalistic video watching. \textit{Taiwanese Psychological Association 2025 Annual Conference}, Tainan, Taiwan. \\[\itemspace]
\noindent Wu, P.-Y. S., \textbf{Chou, F.-C. B.}, Li, C.-C. J., Lo, C.-Y. Y., Chang, C.-Y. E., Wang, T.-R. H., \& Chen, P.-H. A. (2025). The impact of group composition on discussion trajectories. \textit{Taiwanese Psychological Association 2025 Annual Conference}, Tainan, Taiwan. \\[\itemspace]
\noindent Lo, C.-Y. Y., \textbf{Chou, F.-C. B.}, Chang, C.-Y. E., Wu, P.-Y. S., Wang, T.-R. H., \& Chen, P.-H. A. (2025). From watching together to thinking alike: Semantic convergence in shared experience. \textit{Taiwanese Psychological Association 2025 Annual Conference}, Tainan, Taiwan. \\[\itemspace]
\noindent Li, C.-C. J., \textbf{Chou, F.-C. B.}, Wang, T.-R. H., Lin, C.-C. E., \& Chen, P.-H. A. (2025). Longitudinal insights into belief change and psychological adjustment in student peer support groups. \textit{Taiwanese Psychological Association 2025 Annual Conference}, Tainan, Taiwan. \\[\itemspace]
\noindent Wen, Y.-D. W., \textbf{Chou, F.-C. B.} \& Chen, H.-C. (2025). Development and Effectiveness Evaluation of an Online Emotion Regulation Learning Platform. \textit{Taiwanese Association of Clinical Psychology 2025 Annual Conference}, Kaohsiung, Taiwan. \\[\itemspace]
\noindent Lee C.-C. J., \textbf{Chou, F.-C. B.}, Chang, Y.-C. M. \& Chen, P.-H. A. (2025). Exploring the Impact of Belief Changes in Student Mutual Support Group Programs on Well-Being and Self-Efficacy. \textit{Taiwanese Association of Clinical Psychology 2025 Annual Conference}, Kaohsiung, Taiwan. \\[\itemspace]
\noindent Chen, C.-L. W., \textbf{Chou, F.-C. B.}, Hsiao, P.-Y. A., Wang, T.-R. H., \& Chen, P.-H. A. (2025). Uncovering the enduring nature of fear in high trait anxiety with a longitudinal computational affective neuroscience approach. \textit{Social \& Affective Neuroscience Society 2025 Annual Conference}, Chicago, USA. \\[\itemspace]
\noindent Hsiao, P.-Y. A., \textbf{Chou, F.-C. B.}, Chang, C.-Y. E., \& Chen, P.-H. A. (2024). Ideological brains: mapping individual variations in national ideology on variations in brain dynamics during a naturalistic viewing paradigm \textit{Social \& Affective Neuroscience Society 2024 Annual Conference}, Toronto, Canada. \\[\itemspace]
\noindent Chen, Y.-C. C., \textbf{Chou, F.-C. B.}, Jao, C.-Y. M., Chang, C.-Y. E., Liu, Y.-W. J., Chiu, T.-A. P., \& Chen, P.-H. A. (2024). Unveiling Affective Experience during Naturalistic Viewing through Spontaneous Facial Dynamics \textit{Social \& Affective Neuroscience Society 2024 Annual Conference}, Toronto, Canada. \\[\itemspace]
\noindent Chang, C.-Y. E., \textbf{Chou, F.-C. B.}, \& Chen, P.-H. A. (2023). Exploring cross-domain text semantic similarity using large language models. \textit{Taiwanese Psychological Association 2023 Annual Conference}, Hsinchu, Taiwan.\\[\itemspace]
\noindent Lee, W.-T. W., \textbf{Chou, F.-C. B.}, Lin, C. R., \& Chen, P.-H. A. (2022). Taking a machine-learning approach to predict loneliness. \textit{60th Anniversary of Taiwanese Psychological Association Conference}.\\[\itemspace]
\noindent Chiu, T.-A. P., \textbf{Chou, F.-C. B.}, Kuo, Y.-S. A., \& Chen, P.-H. A. (2022). Facial synchrony during naturalistic viewing. \textit{2022 NTU Neurobiology and Cognitive Science Center Summer Internship Conference}.\\[\itemspace]
\noindent Pan, H.-J. S., \textbf{Chou, F.-C. B.}, Huang, Y.-W. Y., Kuo, Y.-S. A., Chen, Y.-C. C., Hsiao, P.-Y. A., Lin, C. R., \& Chen, P.-H. A. (2022). Synchronization of facial behaviors under and after a large-scale social stressor. \textit{Social \& Affective Neuroscience Society 2022 Virtual Conference}.\\[\itemspace]

\vspace{\sectionspace}

\section*{RESEARCH INTERESTS}
\href{https://www.interactingminds.com}{Interacting Minds}, Computational Social Neuroscience, Social Network Analysis, Machine Learning \& Nonverbal Behaviors. \\[\sectionspace]

\vspace{\sectionspace}

\section*{TEACHING ASSISTANT EXPERIENCE}

\noindent\textbf{General Psychology}, National Taiwan University  \hfill 2022, 2023, 2024, 2025
\begin{itemize}
    \item Assisted with lecture preparation, grading, and classroom management.
    \item Held office hours to provide support and guidance for students.
    \item Collaborated with students to help them understand psychological principles, such as cognition, behavior, and development.
\end{itemize}

\noindent\textbf{Personality Psychology}, National Taiwan University \hfill 2023, 2024, 2025
\begin{itemize}
    \item Supported the professor in delivering course material and grading assignments.
    \item Facilitated discussions on key topics, including personality theories and individual differences.
    \item Provided students with additional resources and feedback to help improve their understanding of personality psychology.
\end{itemize}

\vspace{7pt}

\section*{TECHNICAL SKILLS}
\textbf{Programming:} Machine-learning \& Deep-learning (Scikit-learn, Pytorch, TensorFlow), Neuroimaging (Nltools, Nilearn, BrainIAK, fMRIPrep), Non-verbal behavior analysis (Py-Feat, OpenFace, OpenPose), Computational modeling (Numpy, Pandas, R, pymer4, Seaborn, SciPy, MATLAB), Web \& Server programming (JavaScript, Meteor, Node.js, BASH, Socket, SQL), Network analysis (NetworkX), Neurophysiological Signal Processing (NeuroKit), Java, C, C++ \\[\itemspace]
\noindent\textbf{Data Analysis:} RSA (Representational Similarity Analysis), IS-RSA (Intersubject Representational Similarity Analysis), SNA (Social Network Analysis), ML \& DL (Machine Learning \& Deep Learning), TPA (Transition Probability Analysis), ANOVA, GLM, HMM (Hidden Markov Model), Information theory, Linear algebra, Group theory

\thispagestyle{lastupdate}
\end{document}
